Supporting Information for\\ ``A heterogeneous landscape of selection and epistasis in protein-coding genes''

### 2022-03-31 manuscript/supplement.tex
so close

@@

@@

>>>>

% external latex tables
\usepackage{catchfile}
\begin{filecontents*}{AFR.sd1.tex}
\end{filecontents*}

@@

\CatchFileDef{\afrsigned}{AFR.sd1.tex}{}
\begin{table}
    \begin{center}
        \begin{tabular}{lccc}
            \afrsigned
        \end{tabular}
    \end{center}
    \caption{
        \label{tab:afrsd1}
        \textbf{Signed LD in AFR-labeled populations matched to distances
        and allele frequencies of synonymous mutations.}
        Gene-wide signed LD is observed to be at similar slightly positive levels between
        pairs of synonymous and pairs of missense variants. This observation is
        consistest when weighting missense variants to match distances between
        pairs of synonymous variants and when weighting to match synonymous allele
        frequencies, with only a slight reduction in missense \(\sigma_d^1\).
        The distribution of distances between synonymous and missense mutations
        within genes are very similar (Figure~\ref{fig:mutDistances}),
        so matching by distances separating mutations
        has a minor effect on measured average LD.
        The large measurement uncertainty of loss-of-function mutation pairs
        due to few observed pairs of such mutations within the same gene causes
        signed LD to fluctuate when conditioning on distances and frequencies
        matched to synonymous mutations.
    }
\end{table}

\CatchFileDef{\afrsquared}{AFR.sd2.tex}{}
\begin{table}
    \begin{center}
        \begin{tabular}{lccc}
            \afrsquared
        \end{tabular}
    \end{center}
    \caption{
        \label{tab:afrsd2}
        \textbf{Squared LD in AFR-labeled populations matched to distances
        and allele frequencies of synonymous mutations.}
    }
\end{table}

\CatchFileDef{\eursigned}{EUR.sd1.tex}{}
\begin{table}
    \begin{center}
        \begin{tabular}{lccc}
            \eursigned
        \end{tabular}
    \end{center}
    \caption{
        \label{tab:eursd1}
        \textbf{Signed LD in EUR-labeled populations matched to distances
        and allele frequencies of synonymous mutations.}
        Similar to the pattern observed in AFR-labeled populations
        (Table~\ref{tab:afrsd1}), \(sigma_d^1\) between missense mutations matched
        to distances and allele frequencies observed in synonymous mutation pairs
        has only a small effect on average signed LD, and gene-wide measurements
        are roughy equal between these two mutation classes.
        Again, measurement noise for loss-of-function mutation pairs is high.
    }
\end{table}

\CatchFileDef{\eursquared}{EUR.sd2.tex}{}
\begin{table}
    \begin{center}
        \begin{tabular}{lccc}
            \eursquared
        \end{tabular}
    \end{center}
    \caption{
        \label{tab:eursd2}
        \textbf{Squared LD in EUR-labeled populations matched to distances
        and allele frequencies of synonymous mutations.}
    }
\end{table}

\CatchFileDef{\eassigned}{EAS.sd1.tex}{}
\begin{table}
    \begin{center}
        \begin{tabular}{lccc}
            \eassigned
        \end{tabular}
    \end{center}
    \caption{
        \label{tab:eassd1}
        \textbf{Signed LD in EUR-labeled populations matched to distances
        and allele frequencies of synonymous mutations.}
        Similar to the pattern observed in AFR-labeled populations
        (Table~\ref{tab:afrsd1}), \(sigma_d^1\) between missense mutations matched
        to distances and allele frequencies observed in synonymous mutation pairs
        has only a small effect on average signed LD, and gene-wide measurements
        are roughly equal between these two mutation classes. 
        Again, measurement noise for loss-of-function mutation pairs is high.
    }
\end{table}

\CatchFileDef{\eassquared}{EAS.sd2.tex}{}
\begin{table}
    \begin{center}
        \begin{tabular}{lccc}
            \eassquared
        \end{tabular}
    \end{center}
    \caption{
        \label{tab:eassd2}
        \textbf{Squared LD in EAS-labeled populations matched to distances
        and allele frequencies of synonymous mutations.}
    }
\end{table}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics{../figures/mutation_class_distances}
    \caption{
        \textbf{Distances between mutation pairs for different classes of variants.}
        Despite different mutation rates between classes of mutations, the
        proportions of pairs of mutations at given distances are similar.
        Missense mutations, which have the highest mutation rate within genes,
        have slightly more pairs of mutations at close distances than synonymous,
        with loss of function mutations, which have the lowest mutation rate within
        genes, have the fewest pairs at short distances.
    }
    \label{fig:mutDistances}
\end{figure}
